---
title: "Binomial Distribution"
author: "Achintya Suden"
date: "April 30, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}

---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


#Binomial 

*The package `"binomial"` describes perhaps the most famous probability distribution among discrete random variables.    This is the theoretical probability model that we use when calculating probabilities about the number of successes in a fixed number of random trials performed under identical conditions (assuming a constant probability of success on each trial).*

##Binomial Functions 

###Bin Choose
This is a function that calculates the number of combinations  in which *k* successes can occur in *n* trials.
```{r}
#examples include:
#bin_choose(n = 5, k = 2)
#bin_choose(5,0)
#bin_choose(5, 1:3)

bin_choose(n = 5, k = 2)
bin_choose(5,0)
bin_choose(5, 1:3)
```

###Bin Distribution
This is a function that gives you the probability distribution table of the binomial random variable, given a probability and number of trials.
```{r}
#examples include:
#bin_distribution(trials = 5, prob = 0.5)

bin_distribution(trials = 5, prob = 0.5)
```

###Plot Bin Distributon
```{r}
#You can also plot the above probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```



###Bin Cumulative
This is a function that gives you the cumulative distribution table of the binomial random variable, given a probability and number of trials.
```{r}
#examples include:
#bin_cumulative(trials = 5, prob = 0.5)

bin_cumulative(trials = 5, prob = 0.5)
```

###Plot Bin Cumulative
```{r}
#You can also plot the above cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


###Bin Probability
This is a function that calculates the probability of getting k successes in n trials for a binomial random variable.
```{r}
#examples include:
#bin_probability(success = 2, trials = 5, prob = 0.5)
#bin_probability(success = 0:2, trials = 5, prob = 0.5)
#bin_probability(success = 55, trials = 100, prob = 0.45)

bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(success = 55, trials = 100, prob = 0.45)
```


###Bin Variable and Summary of Bin Variable
These are some functions that will summarise (in brief, or in detail) the main aspects  of a binomial random variable, given your inputs for successes, trials, and probability of success.
```{r}
#examples
#bin_variable(3, 0.5)
#bin <- bin_variable(3, 0.5)
#summary.binvar(bin)

bin <- bin_variable(3, 0.5)
bin
summary(bin)


```


###More details of the binomial variable
This are some functions that allow you to extrapolate further descriptive statistics of your binomial random variable.
```{r}
#examples include:
#bin_mean(trials = 10, prob = 0.3)
#bin_variance(trials = 10, prob = 0.3)
#bin_mode(trials = 10, prob = 0.3)
#bin_skewness(trials = 10, prob = 0.3)
#bin_kurtosis(trials = 10, prob = 0.3)

bin_mean(trials = 10, prob = 0.3)
bin_variance(trials = 10, prob = 0.3)
bin_mode(trials = 10, prob = 0.3)
bin_skewness(trials = 10, prob = 0.3)
bin_kurtosis(trials = 10, prob = 0.3)

```


_**These are but a few of the most common funcitonalities of the binomial distribution: play around with this!**_


